### 2020-10-13 manuscript/manuscript.rmd
add cross_validation table
minor changes to the code

@@

![](figures/Extended_Data_Fig7.png)

**Extended Data Fig. 7.** A graphical representation of the posterior probabilities for the 32 analyses presented by Feuda *et al.* in their Table 3. Cells are color coded by whether posterior probability is > 95 for Porifera-sister, > 95 for Ctenophora-sister, or neither (unresolved). Posterior predictive (PP) statistics were estimated for the 16 analyses in the top two rows of this figure (the Chang and full Whelan matrices), but not the bottom two (the Whelan matrices with reduced outgroup sampling).

![](figures/Extended_Data_Fig8.png)

**Extended Data Fig. 8.** The subset of eight GTR+CAT analyses with posterior predictive (PP) scores that is the focus of Feuda *et al.*'s primary conclusions. These are a subset of the 32 analyses presented in their Table 3 and graphically here in the upper right pane. The eight analyses are for two datasets (Chang and Whelan) and four coding schemes. The coding schemes are the original 20 state amino acid data, and three different six state recodings that group amino acids based on different criteria: KGB6, D6, and SR6. Only one of these analyses, the SR6 coding of the Whelan matrix, has > 95 support for Porifera-sister. The 20-state and 6-state points on the plots in Extended Data Fig. 5 correspond to the 20 and SR6 Whelan cells shown here. The presented statistics for these cells are posterior probability of Porifera-sister, Maxdiff (with lower scores indicating better convergence of runs), and five posterior predictive statistics (where lower absolute value indicates better model adequacy). The only one of these eight analyses that provides strong support for Porifera-sister is not the most adequate analysis by any of the posterior predictive scores, and showed the poorest convergence according to Maxdiff.

@@

![](figures/Extended_Data_Fig9.png)
**Extended Data Fig. 10.**
cross_validation =
  read_tsv("../data_processed/tables/cross_validation.tsv") %>%
  gather("model", "score", `nCAT60`, `Poisson-CAT`)

@@

```
```{r}
# https://www.datanovia.com/en/lessons/t-test-in-r/
cross_validation %>%
  group_by(matrix,model) %>%
  get_summary_stats(score, type = "mean_sd")
# Whelan
Dw = cross_validation %>%
  filter(matrix=="Whelan2017_strict")

stat_test_w =
  t.test(score ~ model, var.equal = TRUE, data=Dw)
stat.test_w$p.value

stat.test_p =
    t.test(score ~ model, var.equal = TRUE, data=Dp)
stat.test_p
stat.test_p$p.value
```

>>>>

# https://www.datanovia.com/en/lessons/t-test-in-r/
cross_validation %>%
  group_by(matrix,model) %>%
  get_summary_stats(score, type = "mean_sd")
# Whelan
Dw = cross_validation %>%
  filter(matrix=="Whelan2017_strict")

stat_test_w =
  t.test(score ~ model, var.equal = TRUE, data=Dw)
P_value_Whelan2017_strict=stat.test_w$p.value

stat.test_p =
    t.test(score ~ model, var.equal = TRUE, data=Dp)

P_value_Philippe2009=stat.test_p$p.value
```

@@

![](figures/Extended_Data_Fig10.png)

**Extended Data Fig. 7.** A graphical representation of the posterior probabilities for the 32 analyses presented by Feuda *et al.* in their Table 3 and the subset of eight GTR+CAT analyses with posterior predictive (PP) scores that is the focus of Feuda *et al.*'s primary conclusions. (A). Cells are color coded by whether posterior probability is > 95 for Porifera-sister, > 95 for Ctenophora-sister, or neither (unresolved). Posterior predictive (PP) statistics were estimated for the 16 analyses in the top two rows of this figure (the Chang and full Whelan matrices), but not the bottom two (the Whelan matrices with reduced outgroup sampling). (B). These are a subset of the 32 analyses presented in their Table 3 and graphically here in the upper right pane. The eight analyses are for two datasets (Chang and Whelan) and four coding schemes. The coding schemes are the original 20 state amino acid data, and three different six state recodings that group amino acids based on different criteria: KGB6, D6, and SR6. Only one of these analyses, the SR6 coding of the Whelan matrix, has > 95 support for Porifera-sister. The 20-state and 6-state points on the plots in Extended Data Fig. 5 correspond to the 20 and SR6 Whelan cells shown here. The presented statistics for these cells are posterior probability of Porifera-sister, Maxdiff (with lower scores indicating better convergence of runs), and five posterior predictive statistics (where lower absolute value indicates better model adequacy). The only one of these eight analyses that provides strong support for Porifera-sister is not the most adequate analysis by any of the posterior predictive scores, and showed the poorest convergence according to Maxdiff.

@@

cross_validation =
  read_tsv("../data_processed/tables/cross_validation.tsv") %>%
  gather("model", "score", `nCAT60`, `Poisson-CAT`)

@@

**Extended Data Fig. 10.** Cross validation..
